A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-17 src/tex/ms.tex
Updates from Overleaf

\citet{palla_chemical_2020} explored radial gas flows, variable star formation efficiency of the thin disk, and the onset time of the second infall (but not the infall timescales). They find that inside-out formation (i.e., longer infall timescales in the outer disk) is not sufficient to reproduce observed abundance gradients, and that radial gas flows, possibly in combination with a radially-varying star formation law, are key. Pre-enriched infall in the inner disk ($R<8$ kpc) at the level of -0.5 dex also improves agreement with data.

@@

\begin{table*}
    \centering
    \caption{Sample selection parameters and median uncertainties from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
    \label{tab:sample}
    \begin{tabular}{lll}
        \hline\hline
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range or Value} & \multicolumn{1}{c}{Notes} \\
        \hline
        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15$ kpc    & Eliminate bulge \& extreme outer-disk stars \\
        $|z|$               & $|z| < 2$ kpc                 & Eliminate halo stars \\
        \hline
    \end{tabular}
\end{table*}

@@

We obtain a sample of \input{output/sample_size.txt} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}. We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog. When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122$ kpc \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8$ pc \citep{bennett_vertical_2019}. Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width. \todo{Mention calibrated abundances.}

\todo{Taken from last paper.} We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations. Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10$ Gyr as they do in astroNN \citep{mackereth_dynamical_2019}. We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt} APOGEE stars with age estimates. We note that we use the full sample of \input{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates. Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).

@@

We run multi-zone GCE models using the Versatile Integrator for Chemical Evolution \citep[{\tt VICE};][]{johnson_impact_2020}. The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}. We set up a disk with radial extent $0\leq R_{\rm gal}<20$ kpc that is divided into concentric rings of width $\delta R_{\rm gal}=100$ pc. We use a time-step size of $\Delta t=10$ Myr and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2$ Gyr.

Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling. Stellar populations migrate between zones as described in Section \ref{sec:migration}, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones. We inhibit star formation past $R_{\rm gal}>15.5$ kpc, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population. We also assign a final midplane distance to each stellar population as described in Section \ref{sec:migration}. We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.

@@

The SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
        0 & t < t_D,
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
where $t_D=40$ Myr is the minimum SN Ia delay time, $t_{\rm max}=13.2$ Gyr is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD. Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}
We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.

@@

Figure \ref{fig:yield-outflow} illustrates the effect of the yield scaling on the abundance evolution in one-zone models. All models feature a rapid dilution of the ISM metallicity by $\sim0.5-0.8$ dex, visible in the top two panels, brought on by the infall of pristine gas at $t_{\rm max}$. For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the present day. The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5$ Gyr ago. However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.

Figure \ref{fig:yield-outflow} also indicates the mode of the APOGEE abundance distributions in 1 Gyr-wide age bins. As explained by \citet{johnson_milky_2024}, the mode is expected to be less sensitive to the effects of radial migration than other statistical measures. The data show that the evolution in [O/H] is close to flat over the past 5 Gyr. The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model shows significant evolution of $\sim0.2$ dex during the same time period. The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia. Between lookback times of $\sim5-9$ Gyr, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times. The [O/Fe] evolution of all three models is nearly identical over the past 5 Gyr, and shows a similar evolution to the data apart from a $\sim0.05$ dex offset. \todo{Is this offset a problem? I could raise the SN Ia yields, but the global distributions would not match quite as well.}

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{The abundance evolution of three one-zone models with different yield and outflow settings. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq|z|\leq0.5$ kpc) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
    \label{fig:yield-outflow}
\end{figure}

@@

We adopt a fiducial prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\odot=8$ kpc. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
\begin{equation}
    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}.
\end{equation}
We adopt $R_\eta=7.2$ kpc as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
\todo{Motivate exponential scale radius.}

@@

The infall rate is described by two successive, exponentially declining bursts in time. The first infall component induces the formation of the thick disk, and the second component produces the thin disk. At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
\end{equation}
where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall, and $f_{2/1}$ is the ratio of the second infall amplitude to the first. We calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
\begin{equation}
    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_{\Sigma,0} e^{R(1/R_2 - 1/R_1)}.
\end{equation}
We adopt a thick disk scale radius of $R_1=2.0$ kpc, a thin disk scale radius of $R_2=2.5$ kpc, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.

In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$). However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, either from gas stripped from dwarf galaxies or from SNe in the halo \todo{(citations; any measurements of CGM metallicity?)}. For this reason, we also test cases where the infalling gas is pre-enriched and its metallicity is described by
\begin{equation}
    \label{eq:pre-enrichment}
    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{{\rm [X/H]}_{\rm CGM}}.
\end{equation}
In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2$ Gyr and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$. We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.

@@

% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1$ Gyr, $\tau_2\sim3-10$ Gyr, and $t_{\rm max}\sim3-5$ Gyr. 
Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model. The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence. Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6$ Gyr. We adopt $\tau_1=1$ Gyr for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx+0.3$.

Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that 
% the second infall timescale $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions. 
the second infall timescale $\tau_2$ controls the width of the MDF and the low-$\alpha$ [O/Fe] distribution. A shorter $\tau_2$ produces a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces both a narrower low-$\alpha$ sequence and a narrower MDF. We note that our maximum value of $\tau_2=30$ Gyr is very close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns. Between $\tau_2=3-30$ Gyr, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood. We adopt a fiducial value of $\tau_2=15$ Gyr for the Solar neighborhood in order to minimize the width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times. This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}. 
% In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.

In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk. Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1$ Gyr in the inner disk and $\tau_2=7$ Gyr at the Solar annulus. This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}. We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15$ Gyr at the Solar annulus and a scale radius $R_{\tau_2}=7$ kpc. This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}. We also run models with a linear prescription and with a uniform value for $\tau_2$ and find little difference in our key results.

Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2$ Gyr, but in this case the gas tracks do not produce the characteristic abundance loop. For $t_{\rm max}>2$ Gyr, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different. The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}. We adopt a fiducial value of $t_{\rm max}=4.2$ Gyr so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05$ Gyr \citep{pinsonneault_apokasc-3_2024}. This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.

@@

The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
\begin{equation}
    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61},
    \label{eq:radial-migration}
\end{equation}
where we adopt $\sigma_{\rm RM8}=2.68$ kpc as the fiducial value for the strength of radial migration. This is smaller than the value of $\sigma_{\rm RM8}=3.6$ kpc found by \citet{frankel_measuring_2018}, but in \todo{Section X} we explore the effect of a stronger migration prescription.

@@

@@

>>>>

\citet{palla_chemical_2020} explored radial gas flows, variable star formation efficiency of the thin disk, and the onset time of the second infall (but not the infall timescales). They find that inside-out formation (i.e., longer infall timescales in the outer disk) is not sufficient to reproduce observed abundance gradients, and that radial gas flows, possibly in combination with a radially-varying star formation law, are key. Pre-enriched infall in the inner disk ($R<8\,{\rm kpc}$) at the level of -0.5 dex also improves agreement with data.

@@

\begin{table*}
    \centering
    \caption{Sample selection parameters and median uncertainties from APOGEE DR17 (see Section \ref{sec:observational-sample}).}
    \label{tab:sample}
    \begin{tabular}{lll}
        \hline\hline
        \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range or Value} & \multicolumn{1}{c}{Notes} \\
        \hline
        $\log g$            & $1.0 < \log g < 3.8$          & Select giants only \\
        $T_{\rm eff}$       & $3500 < T_{\rm eff} < 5500$ K & Reliable temperature range \\
        $S/N$               & $S/N > 80$                    & Required for accurate stellar parameters \\
        ASPCAPFLAG Bits     & $\notin$ 23                   & Remove stars flagged as bad \\
        EXTRATARG Bits      & $\notin$ 0, 1, 2, 3, or 4     & Select main red star sample only \\
        Age                 & $\sigma_{\rm Age} < 40\%$     & Age uncertainty from \citetalias{leung_variational_2023} \\
        $R_{\rm gal}$     & $3 < R_{\rm gal} < 15\,{\rm kpc}$    & Eliminate bulge \& extreme outer-disk stars \\
        $|z|$               & $|z| < 2\,{\rm kpc}$                 & Eliminate halo stars \\
        \hline
    \end{tabular}
\end{table*}

@@

We obtain a sample of \input{output/sample_size.txt} red giant branch and red clump stars with high-quality spectra using the selection criteria listed in Table \ref{tab:sample}, which are adapted from \citet{hayden_chemical_2015}. We use the \citet{bailer-jones_estimating_2021} photo-geometric distance estimates from {\it Gaia} Early Data Release 3 \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2021} included in the APOGEE DR17 catalog. When calculating the galactocentric radius $R_{\rm gal}$ and midplane distance $z$ of each star, we assume the distance between the Sun and the Galactic center is $R_\odot=8.122\,{\rm kpc}$ \citep{gravity_collaboration_detection_2018} and the Solar midplane distance is $z_\odot=20.8\,{\rm pc}$ \citep{bennett_vertical_2019}. Table \ref{tab:apogee-regions} presents the number of APOGEE stars in bins of $R_{\rm gal}$ and $|z|$; typical distance uncertainties are much smaller than the bin width. \todo{Mention calibrated abundances.}

\todo{Taken from last paper.} We use estimated ages from \citet[][hereafter \citetalias{leung_variational_2023}]{leung_variational_2023}, who use a variational encoder-decoder network which is trained on asteroseismic data to retrieve age estimates for APOGEE giants without contamination from age-abundance correlations. Importantly, the \citetalias{leung_variational_2023} ages do not plateau beyond $\sim10\,{\rm Gyr}$ as they do in astroNN \citep{mackereth_dynamical_2019}. We use an age uncertainty cut of 40\% per the recommendations of \citetalias{leung_variational_2023}, which produces a total sample of \input{output/age_sample_size.txt} APOGEE stars with age estimates. We note that we use the full sample of \input{output/sample_size.txt} APOGEE stars unless we explicitly compare to age estimates. Table \ref{tab:uncertainties} presents the median and dispersion ($95^{\rm th} - 5^{\rm th}$ percentile difference) of the uncertainty in [Fe/H], [O/Fe], and log(age).

@@

We run multi-zone GCE models using the Versatile Integrator for Chemical Evolution \citep[{\tt VICE};][]{johnson_impact_2020}. The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}. We set up a disk with radial extent $0\leq R_{\rm gal}<20\,{\rm kpc}$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$. We use a time-step size of $\Delta t=10\,{\rm Myr}$ and a resolution of $n=8$ stellar populations per time-step per ring, and we run our models up to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$.

Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling. Stellar populations migrate between zones as described in Section \ref{sec:migration}, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones. We inhibit star formation past $R_{\rm gal}>15.5\,{\rm kpc}$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population. We also assign a final midplane distance to each stellar population as described in Section \ref{sec:migration}. We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}.

@@

The SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
        0 & t < t_D,
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
where $t_D=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm max}=13.2\,{\rm Gyr}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD. Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}
We discuss the implications of using a different DTD in Section \ref{sec:abundance-distributions}.

@@

Figure \ref{fig:yield-outflow} illustrates the effect of the yield scaling on the abundance evolution in one-zone models. All models feature a rapid dilution of the ISM metallicity by $\sim0.5-0.8$ dex, visible in the top two panels, brought on by the infall of pristine gas at $t_{\rm max}$. For the model with $y/Z_\odot=1$, this dilution persists for some time and the metallicity does not return to Solar until the present day. The models with higher yields and outflows recover from this dilution more quickly, returning to Solar metallicity by $\sim5\,{\rm Gyr}$ ago. However, the high-yield models experience a decline in [O/Fe] of $\sim0.2$ dex between the second infall and the present day, contrasted with the smaller decline of $\sim0.1$ dex in the low-yield model.

Figure \ref{fig:yield-outflow} also indicates the mode of the APOGEE abundance distributions in 1 Gyr-wide age bins. As explained by \citet{johnson_milky_2024}, the mode is expected to be less sensitive to the effects of radial migration than other statistical measures. The data show that the evolution in [O/H] is close to flat over the past 5 Gyr. The behavior of the $y/Z_\odot=2$ and $y/Z_\odot=3$ models closely matches this trend in the data, whereas the $y/Z_\odot=1$ model shows significant evolution of $\sim0.2$ dex during the same time period. The [Fe/H] abundance in the data does increase slightly at late times, likely due to the delayed contribution of Fe from SNe Ia. Between lookback times of $\sim5-9\,{\rm Gyr}$, the modes of [O/H] and [Fe/H] are actually higher than the present-day, likely due to a larger population of migrated stars relative to stars born in-situ at those times. The [O/Fe] evolution of all three models is nearly identical over the past 5 Gyr, and shows a similar evolution to the data apart from a $\sim0.05$ dex offset. \todo{Is this offset a problem? I could raise the SN Ia yields, but the global distributions would not match quite as well.}

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{The abundance evolution of three one-zone models with different yield and outflow settings. Table \ref{tab:yields} presents the population-averaged yields for each model. The gray points with error bars indicate the mode of the APOGEE abundance distributions from the Solar neighborhood ($7\leq R_{\rm gal}\leq 9\,{\rm kpc}$, $0\leq|z|\leq0.5\,{\rm kpc}$) in 1 Gyr-wide bins of the \citet{leung_variational_2023} age estimates.}
    \label{fig:yield-outflow}
\end{figure}

@@

We adopt a fiducial prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\odot=8\,{\rm kpc}$. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
\begin{equation}
    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}.
\end{equation}
We adopt $R_\eta=7.2\,{\rm kpc}$ as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
\todo{Motivate exponential scale radius.}

@@

The infall rate is described by two successive, exponentially declining bursts in time. The first infall component induces the formation of the thick disk, and the second component produces the thin disk. At a given galactocentric radius $R_{\rm gal}$, the un-normalized form of the infall rate is
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm in}(t|R_{\rm gal}) = e^{-t/\tau_1} + f_{2/1}(R_{\rm gal}) e^{-(t-t_{\rm max})/\tau_2},
\end{equation}
where $\tau_1$ and $\tau_2$ are the first and second infall timescales, respectively, $t_{\rm max}$ is the onset of the second infall and thus the time of maximum gas infall, and $f_{2/1}$ is the ratio of the second infall amplitude to the first. We calculate $f_{2/1}$ for each zone such that the resulting stellar density profile follows a two-component disk, with the surface density ratio of the thick and thin disks given by
\begin{equation}
    f_\Sigma(R) \equiv \frac{\Sigma_1(R)}{\Sigma_2(R)} = f_{\Sigma,0} e^{R(1/R_2 - 1/R_1)}.
\end{equation}
We adopt a thick disk scale radius of $R_1=2.0\,{\rm kpc}$, a thin disk scale radius of $R_2=2.5\,{\rm kpc}$, and a central surface density ratio of $f_{\Sigma,0}=0.27$ \citep{bland-hawthorn_galaxy_2016}.

In most of our models, we assume the infalling gas is pristine (i.e., $Z_{\rm in}=0$). However, the circumgalactic medium (CGM) from which the infalling gas is drawn could be previously enriched, either from gas stripped from dwarf galaxies or from SNe in the halo \todo{(citations; any measurements of CGM metallicity?)}. For this reason, we also test cases where the infalling gas is pre-enriched and its metallicity is described by
\begin{equation}
    \label{eq:pre-enrichment}
    Z_{\rm in}(t) = (1 - \exp(-t/\tau_{\rm rise})) Z_\odot 10^{{\rm [X/H]}_{\rm CGM}}.
\end{equation}
In this case, the metallicity rises from 0 with a timescale $\tau_{\rm rise}=2\,{\rm Gyr}$ and plateaus at ${\rm [X/H]}_{\rm CGM}={\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}$. We also investigate cases where the CGM is $\alpha$-enhanced, i.e., ${\rm [O/Fe]}_{\rm CGM}>0$.

@@

% The parameters of Equation \ref{eq:infall-rate} have important effects on the chemical evolution of the model. 
% Previous studies of the two-infall model have adopted values for the infall parameters of $\tau_1\sim0.1-1\,{\rm Gyr}$, $\tau_2\sim3-10\,{\rm Gyr}$, and $t_{\rm max}\sim3-5\,{\rm Gyr}$. 
Figure \ref{fig:twoinfall-parameters} illustrates the effect of varying the infall parameters on gas abundance tracks and stellar abundance distributions in a one-zone model. The first infall timescale $\tau_1$, shown in panel (a), primarily affects the stellar distribution along the high-$\alpha$ sequence. Though $\tau_1$ has an apparently large effect on the size of the low-$\alpha$ loop, the effect on the stellar abundance distribution of the low-$\alpha$ sequence is quite small due to the low number of stars formed between $t\sim3-6\,{\rm Gyr}$. We adopt $\tau_1=1\,{\rm Gyr}$ for our fiducial value, in line with \citet{spitoni_galactic_2020} but longer than, e.g., \citet{nissen_high-precision_2020} or \citet{spitoni_apogee_2021}, in order to set the peak of the high-$\alpha$ sequence at ${\rm [O/Fe]}\approx+0.3$.

Panel (b) of Figure \ref{fig:twoinfall-parameters} shows that 
% the second infall timescale $\tau_2$ is the most important parameter to tune in order to reproduce the observed stellar abundance distributions. 
the second infall timescale $\tau_2$ controls the width of the MDF and the low-$\alpha$ [O/Fe] distribution. A shorter $\tau_2$ produces a broader [O/Fe] distribution which is skewed to higher [O/Fe], while a longer $\tau_2$ produces both a narrower low-$\alpha$ sequence and a narrower MDF. We note that our maximum value of $\tau_2=30\,{\rm Gyr}$ is very close to a constant infall rate, so a further increase in $\tau_2$ has diminishing returns. Between $\tau_2=3-30\,{\rm Gyr}$, the endpoint of the abundance tracks shifts by $\sim0.2$ dex in [Fe/H] and $\sim0.1$ dex in [O/Fe], which could affect the model's ability to reproduce the present-day abundance of the Solar neighborhood. We adopt a fiducial value of $\tau_2=15\,{\rm Gyr}$ for the Solar neighborhood in order to minimize the width of the low-$\alpha$ [O/Fe] distribution while still approaching Solar [Fe/H] at late times. This value is in line with the infall timescale recovered by \citet{spitoni_galactic_2020}, and similar to the local star formation timescale adopted by \citet{johnson_stellar_2021}, but significantly longer than the timescales found by \citet{nissen_high-precision_2020} and \citet{spitoni_apogee_2021}. 
% In \todo{Section X}, we explore the effect of varying $\tau_2$ with radius in multi-zone models.

In our multi-zone models, we vary the second infall timescale with radius to produce inside-out growth of the disk. Previous multi-zone two-infall studies \citep[e.g.,][]{chiappini_abundance_2001,palla_chemical_2020} scale $\tau_2$ linearly with radius, with $\tau_2\approx1\,{\rm Gyr}$ in the inner disk and $\tau_2=7\,{\rm Gyr}$ at the Solar annulus. This prescription was adopted to match the metallicity distribution of the Solar neighborhood and the bulge in the absence of mass-loaded outflows \citep{romano_mass_2000}. We instead adopt an exponential $\tau_2 - R_{\rm gal}$ relation, with $\tau_2(R_\odot)=15\,{\rm Gyr}$ at the Solar annulus and a scale radius $R_{\tau_2}=7\,{\rm kpc}$. This is similar to the star formation history timescale of \citet{johnson_stellar_2021}, which was based on the  stellar age gradients in Milky Way-like spirals observed by \citet{sanchez_spatially_2020}. We also run models with a linear prescription and with a uniform value for $\tau_2$ and find little difference in our key results.

Finally, panel (c) of Figure \ref{fig:twoinfall-parameters} shows that the time of maximum infall $t_{\rm max}$ (c) strongly affects the overall stellar abundance distribution for values $t_{\rm max}\leq2\,{\rm Gyr}$, but in this case the gas tracks do not produce the characteristic abundance loop. For $t_{\rm max}>2\,{\rm Gyr}$, varying $t_{\rm max}$ results in a minor shift to the mean of the MDF and little change to the [O/Fe] distributions, even though the abundance tracks in [O/Fe]--[Fe/H] space appear very different. The value of $t_{\rm max}$ also slightly adjusts the ISM abundance endpoint, as a longer $t_{\rm max}$ means the chemical evolution ``reset'' from the second infall occurs closer to the present day (see discussion in Section \ref{sec:age-abundance}. We adopt a fiducial value of $t_{\rm max}=4.2\,{\rm Gyr}$ so that the second infall occurs at a lookback time of 9 Gyr, younger than the median age of the thick disk in the APOKASC-3 catalog of $9.14\pm0.05\,{\rm Gyr}$ \citep{pinsonneault_apokasc-3_2024}. This value is generally in line with previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020,spitoni_galactic_2020,spitoni_apogee_2021}.

@@

The distance a stellar population born at $R_{\rm form}$ migrates over its age $\tau$ is drawn from a Gaussian centered at 0 with standard deviation
\begin{equation}
    \sigma_{\rm RM} = \sigma_{\rm RM8} \Big(\frac{\tau}{8\,{\rm Gyr}}\Big)^{0.33} \Big(\frac{R_{\rm form}}{8\,{\rm kpc}}\Big)^{0.61},
    \label{eq:radial-migration}
\end{equation}
where we adopt $\sigma_{\rm RM8}=2.68\,{\rm kpc}$ as the fiducial value for the strength of radial migration. This is smaller than the value of $\sigma_{\rm RM8}=3.6\,{\rm kpc}$ found by \citet{frankel_measuring_2018}, but in Section \ref{sec:age-abundance} we explore the effect of a stronger migration prescription.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
    \caption{Evolution of the MDF across the Galactic disk.}
    \label{fig:mdf-evolution}
\end{figure*}

@@

Radial gas flows are hard :'(
